BioTime

### 2020-09-08 data-raw/biotime.Rmd
Switch to base R read csv to avoid parsing failures

Import occurence data from Biotime
```{r}
#rdataretriever::install("biotime", connection = "csv", data_dir = here("data"))
# 
# data <- read_csv(system.file("extdata", "biotime/biotime_metadata.csv", package = "biodivTS")) %>%
#   select(study_id, taxa) %>%
#   left_join(read_csv(system.file("extdata", "biotime/biotime_query.csv", package = "biodivTS")), by = "study_id")

>>>>

Import occurence data from Biotime
```{r}
#rdataretriever::install("biotime", connection = "csv", data_dir = here("data"))
# 
# data <- read.csv(system.file("extdata", "biotime/biotime_metadata.csv", package = "biodivTS")) %>%
#   select(study_id, taxa) %>%
#   left_join(read.csv(system.file("extdata", "biotime/biotime_query.csv", package = "biodivTS")), by = "study_id")
